\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-13 podc16/paper2.tex
minor

\noindent\textbf{Lemma 2.} \emph{If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible. }

>>>>

\noindent\textbf{Lemma 2.} \emph{If $g_p^1$ is the graph $g_p$ at time $t_1$ and $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible. }
